---
title: "Individual 2"
author: "Hanying Shen"
date: "9/17/2019"
output: html_document
---
Question set (individual)

For each of the questions below provide at least one graphic as a basis for your answer.

1. How are ratings distributed? Don’t forget to mention outliers, if there are any.
```{r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
head(choco)
```
```{r}
hist(choco$Rating, breaks = 10)
```
2. Do ratings depend on the cacao percentage of a chocolate bar?
```{r}
plot(choco$Cocoa.Pct, choco$Rating)
```
No, ratings does not depend on the cacao percentage of a chocolate bar from the chart above.

3. What class is the variable representing company locations? How is this different from a ‘character’ variable? (You do not need to produce a graphic for this question.)
```{r}
class(choco$Company.Location)
```
The class of company locations is factor. A factor variable is the type vector contains a set of numeric codes with character-valued levels, and the character variable builts in character vectors are letters and LETTERS which provide the 26 lower (and upper) case letters, respecitively. 
